PK object batch mode trial

### 2023-08-23 data-raw/batchMode_trial_gpm.Rmd
New parallelized tidy version of do_fit

@@

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

@@

@@

plot(my_pk,
     method = "L-BFGS-B",
     n_interp = 50,

     print_out = TRUE)
# Joint
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

myRMSE <- myRMSE %>%
  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
                median_MSE = median(RMSE^2, na.rm = TRUE))

my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE)
mypl <- ggplot(data = my_df,
               aes(
                 x = within_2fold,
                 y = Rsq,
                 color = model
               )) + geom_point() +
  geom_abline(slope = 1, color = "red4", linetype = "longdash") +
  scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
ggExtra::ggMarginal(mypl, groupFill = TRUE,
                    type = "histogram",
                    xparams = list(binwidth = 0.05),
                    yparams = list(binwidth = 0.05))
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "R2_within2fold_comparison.png"),
       plot = ggExtra::ggMarginal(mypl, groupFill = TRUE,
                    type = "histogram",
                    xparams = list(binwidth = 0.05),
                    yparams = list(binwidth = 0.05)),
       height = 5,
       width = 5,
       units = "in")

ggplot(data = rmse(my_pk, method = "L-BFGS-B",
                   rmse_group = vars(Route, Media, Dose),
                   use_scale_conc = FALSE) %>%
         inner_join(winning_model) %>%
         mutate(RMSE = ifelse(RMSE == 0, 1E-6, RMSE)),
               aes(
                 x = log10(RMSE),
                 color = model,
                 fill = model
               )) + 
  geom_histogram(bins = 100) +
  # geom_freqpoly(aes(groups = paste(Chemical, Species)),
  #               color = "black",
  #               bins = 5) +
  scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
  scale_fill_manual(values = c("#0398FC", "#D68E09", "grey10")) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  facet_grid(rows = vars(model),
             cols = vars(Route)) +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        strip.background = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RMSEs_winningmodel_LBFGSB_zero1E-6_RouteFacet_notNormalized.png"),
       height = 4,
       width = 6,
       units = "in")

@@

>>>>

# Reasonable fits... multiple species
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                              "DTXSID8025337"))

@@

```{r single_fit}
# Pooled
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
# Add Reference for Joint Analysis

@@

my_pk <- do_prefit(my_pk) # needs reframe somewhere
# Timing for normal fit sapply
{
  start_t <- Sys.time()
  normal_fit <- do_fit(my_pk)
  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
} 
# Timing for multidplyr
{
  start_t <- Sys.time()
  party_fit <- do_fit(my_pk)
  round(Sys.time() - start_t, 3) # 2.514min (5 data_groups)
}
my_pk <- do_fit(my_pk)

@@

plot(my_pk,
     method = "L-BFGS-B",
     n_interp = 20,
     print_out = TRUE)
# Joint
my_pk <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
# Add Reference for Joint Analysis

@@

myRMSE_all <- myRMSE %>%
  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
                median_MSE = median(RMSE^2, na.rm = TRUE))

my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE_all)
mypl <- ggplot(data = my_df,
               aes(
                 x = within_2fold,
                 y = Rsq,
                 color = model
               )) +
  geom_point() +
  geom_abline(slope = 1, color = "red4", linetype = "longdash") +
  scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
  labs(x = "% Fold Error within 2-fold",
       y = "R-squared value") +
  theme(aspect.ratio = 1,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key = element_blank())
panelA_plot <- ggExtra::ggMarginal(mypl, groupFill = TRUE,
                    type = "histogram",
                    xparams = list(binwidth = 0.05),
                    yparams = list(binwidth = 0.05))
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "R2_within2fold_comparison.png"),
       plot = ggExtra::ggMarginal(mypl, groupFill = TRUE,
                    type = "histogram",
                    xparams = list(binwidth = 0.05),
                    yparams = list(binwidth = 0.05)),
       height = 5,
       width = 5,
       units = "in")

panelB_plot <- ggplot(data = myRMSE %>%
         inner_join(winning_model) %>%
         mutate(RMSE = ifelse(RMSE == 0, NA, RMSE)),
               aes(
                 x = log10(RMSE),
                 color = model,
                 fill = model
               )) + 
  geom_histogram(bins = 100) +
  labs(y = "Count") +
  scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
  scale_fill_manual(values = c("#0398FC", "#D68E09", "grey10")) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  facet_grid(rows = vars(model),
             cols = vars(Route)) +
  theme(aspect.ratio = 0.5,
        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        strip.background = element_blank(),
        legend.position = "none",
        legend.title = element_blank())
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RMSEs_winningmodel_LBFGSB_zero1E-6_RouteFacet_notNormalized.png"),
       height = 4,
       width = 6,
       units = "in")

cowplot::plot_grid(panelA_plot, panelB_plot, labels = c("A", "B"))
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "CombinedPlot_Rsquared_RMSE.png"),
       height = 5,
       width = 7.45,
       bg = "white",
       units = "in")

@@

This chunk is to run all the options through a
standard pipeline that calculates RMSE for Cmax and AUC_inf
for the Chemical Species Route Media grouping...

```{r pooled_fitting_choices}
# Types of Choices:
## Dose Normalized
## Log10 transform
## Scale time

# Pooled
my_pk_000p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_100p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_110p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_111p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_010p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_011p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_001p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk_101p <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

```{r joint_fitting_choices}
# Joint
my_pk_000j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_100j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_110j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_111j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_010j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_011j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_001j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

my_pk_101j <- pk(data = cvt) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = FALSE,
                      suppress.messages = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
```

```{r}
## Do fits
my_pk_000p <- do_fit(my_pk_000p)
my_pk_100p <- do_fit(my_pk_100p)
my_pk_110p <- do_fit(my_pk_110p)
my_pk_111p <- do_fit(my_pk_111p)
my_pk_010p <- do_fit(my_pk_010p)
my_pk_011p <- do_fit(my_pk_011p)
my_pk_001p <- do_fit(my_pk_001p)
my_pk_101p <- do_fit(my_pk_101p)

## Do fits
my_pk_000j <- do_fit(my_pk_000j)
my_pk_100j <- do_fit(my_pk_100j)
my_pk_110j <- do_fit(my_pk_110j)
my_pk_111j <- do_fit(my_pk_111j)
my_pk_010j <- do_fit(my_pk_010j)
my_pk_011j <- do_fit(my_pk_011j)
my_pk_001j <- do_fit(my_pk_001j)
my_pk_101j <- do_fit(my_pk_101j)
```

```{r Evaluating_Choices}
# Evaluation
# Current: my_pk_111p

get_choices <- function(obj, PJ = "Pooled") {
  dose_norm <- obj$scales$conc$dose_norm
  log10_norm <- obj$scales$conc$log10_trans
  time_scale <- ifelse(obj$scales$time$new_units == "identity", FALSE, TRUE)

  my_choices <- paste0(dose_norm+0,
                       log10_norm+0,
                       time_scale+0,
                       " ", PJ)
  return(my_choices)
}

# Write into package
evaluate_choices <- function(obj) {
  pk_name <- get_choices(obj)

  cli::cli_progress_step("Winning Model...")
  # Wide winning model
  suppressMessages({
    winning_model <- get_winning_model(obj = obj) %>%
      group_by(method, model) %>%
      count() %>%
      pivot_wider(names_from = model, values_from = n) %>%
      mutate(Options = pk_name)
  })

  cli::cli_progress_step("Cmax and AUC_inf RMSEs...")
  # Cmax and AUC_inf RMSEs
  suppressMessages({
    RMSE_eval <- eval_tkstats(obj = obj) %>%
    mutate(Options = pk_name) %>%
    dplyr::select(Options,
                Chemical, Species,
                Route, Media, Reference,
                method, model,
                starts_with("Cmax"),
                starts_with("AUC_inf")) %>%
  rowwise() %>%
  mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
         SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
  filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
  group_by(Options, method) %>%
  summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
                             na.rm = FALSE)) %>% signif(digits = 4),
            RMSE_AUC = sqrt(mean(SE_AUC_inf,
                            na.rm = FALSE)) %>% signif(digits = 4))
  })

  cli::cli_progress_step("More detailed metrics...")
  # Other metrics (detailed)
  suppressMessages({
    r2_df <- rsq(obj, use_scale_conc = FALSE) %>%
    inner_join(winning_model)
  myAIC <- AIC(obj) %>%
    inner_join(winning_model)
  fold_errors_all <- fold_errors(obj) %>%
    inner_join(winning_model) %>%
    dplyr::filter(Detect %in% TRUE) %>%
    dplyr::group_by(!!!obj$data_group, model, method) %>%
    dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE) %>%
                       signif(digits = 4),
                     median_FoldErr = median(Fold_Error, na.rm = TRUE) %>%
                       signif(digits = 4),
                     within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error) %>%
                       signif(digits = 4))

  myRMSE_all <- rmse(obj,
                     rmse_group = vars(Route, Media, Dose),
                     use_scale_conc = FALSE) %>% 
    inner_join(winning_model) %>%
    dplyr::group_by(!!!obj$data_group, model, method) %>%
    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4),
                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
                       signif(digits = 4))

  my_df <- left_join(fold_errors_all, r2_df) %>%
    inner_join(myAIC) %>%
    inner_join(myRMSE_all) %>%
    mutate(Options = pk_name, .before = Chemical)

  full_list <- list(winning_model, RMSE_eval, my_df)
  })

  return(full_list)
}
gc()

my_pk_000p <- evaluate_choices(my_pk_000p) # Done
my_pk_100p <- evaluate_choices(my_pk_100p) # Done
my_pk_110p <- do_fit(my_pk_110p) %>% evaluate_choices() # Done
my_pk_111p <- do_fit(my_pk_111p) %>% evaluate_choices() # Done
my_pk_010p <- do_fit(my_pk_010p) %>% evaluate_choices() # Done
my_pk_011p <- do_fit(my_pk_011p) %>% evaluate_choices() # Done (took 1.807 hrs)
my_pk_001p <- do_fit(my_pk_001p) %>% evaluate_choices() # Done

my_pk_101p <- do_data_info(my_pk_101p) # This took 13 min

my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices()

# Run after each evaluation
# initialization (only run once)
winning_model_final <- NULL
rmse_summary <- NULL
detail_stats <- NULL

# Run all at once
{
current_pk <- my_pk_101p # Define current evaluated pk object here
winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
rmse_summary <- bind_rows(rmse_summary, current_pk[[2]])
detail_stats <- bind_rows(detail_stats, current_pk[[3]])
rm(current_pk)
gc()
}

# For copy + pasting into Excel workbook
winning_model_final %>% clipr::write_clip(col.names = FALSE)
clipr::clear_clip()
rmse_summary %>% clipr::write_clip(col.names = FALSE)
clipr::clear_clip()
detail_stats %>% clipr::write_clip(col.names = FALSE)
clipr::clear_clip()
gc()
```
